### 2024-03-25 Introduction+SummaryStats.Rmd
fixed names

```{r}
library(ggplot2)
library(readxl)
library(cowplot)
library(tidyverse)
library(lubridate)
library(dplyr)
```

@@

```{r}
SummarySeasonSummer <- SummarySeason |>
  filter(Season == "Winter")
print(SummarySeasonSummer)
```

```{r}
SummarySeasonSummer <- SummarySeason |>
  filter(Season == "Spring")
print(SummarySeasonSummer)
```

```{r}
SummarySeasonSummer <- SummarySeason |>
  filter(Season == "Fall")
print(SummarySeasonSummer)
```

>>>>

```{r}
library(ggplot2)
library(readxl)
library(cowplot)
library(tidyverse)
library(lubridate)
library(dplyr)
library(knitr)
```

@@

```{r}
SummarySeasonWinter <- SummarySeason |>
  filter(Season == "Winter")
print(SummarySeasonSummer)
```

```{r}
SummarySeasonSpring <- SummarySeason |>
  filter(Season == "Spring")
print(SummarySeasonSummer)
```

```{r}
SummarySeasonFall <- SummarySeason |>
  filter(Season == "Fall")
print(SummarySeasonSummer)
```
